3D Magnetic modelling of ellipsoidal bodies

### 2017-01-26 manuscript/manuscript.tex
depolarization tensor N dagger for all ellipsoids

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
factors are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$,
$\cos \phi = c/a$,
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: .
\label{eq:E-kappa-phi}
\end{equation}
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetization factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas, but without any proof.

@@

For prolate ellipsoids (e.g., $a > b = c$), the demagnetization
factors are given by
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
- 1 \right\rbrace
\label{eq:n-tilde-dagger-11-prolate}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
\label{eq:n-tilde-dagger-22-prolate}
\end{equation}
where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
Equation \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
The detailed deduction of the demagnetization factors 
$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
can be found in \citet{stoner1945}. These formulas were posteriorly 
presented by \citet{emerson1985}, but without any mathematical proof.

@@

For oblate ellipsoids (e.g., $a < b = c$), the demagnetization
factors are given by
\begin{equation}
\tilde{n}^{\dagger}_{11} = 
\frac{1}{1 - m^{2}} \left[
1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
\right] \: ,
\label{eq:n-tilde-dagger-11-oblate}
\end{equation}
where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
are calculated according to
\ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
defined in Equation \ref{eq:n-tilde-dagger-11-oblate}), 
and $m = a/b$.
The detailed deduction of these demagnetization factors 
can be found in \citet{stoner1945}. These formulas can also be found
in \citet{emerson1985}, but without any mathematical proof.
The only difference, however, is that \citet{emerson1985} replaced
the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
the trigonometric identity 
$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.

@@

The elements of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
produced by the ellipsoid (Eq. \ref{eq:delta-H-tilde}) and
the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
are calculated according to Equation \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).

@@

In the case of oblate ellipsoids, the procedure for determining
the parameter $\lambda$ is very similar to that one for prolate
ellipsoids.
The semi-axes $a$, $b$, $c$ of oblate 
ellipsoids are defined so that $b = c > a > 0$
and the condition that must be fulfilled by 
the variable $u$ is $u + a^{2} > 0$.
In this case, the two roots of the resulting quadratic equation 
lie in the intervals $[ -b^{2} \, , -a^{2} ]$ and $[ -a^{2} \, , \infty [$.
Consequently, we are still interested in the largest root of
the quadratic equation for the variable $u$, which is also 
calculated by using Equation \ref{eq:lambda-prolate-ell}.

@@

Let us first consider a triaxial ellipsoid. In this case,
the spatial derivatives of $\lambda$ are given by
\begin{equation}
\frac{\partial \lambda}{\partial \tilde{r}_{j}} =
\frac{\frac{2 \, \tilde{r}_{j}}{\left( e_{j}^{2} + \lambda \right)}}{
\left( \frac{\tilde{x}}{a^{2} + \lambda}\right)^{2} +
\left( \frac{\tilde{y}}{b^{2} + \lambda}\right)^{2} + 
\left( \frac{\tilde{z}}{c^{2} + \lambda}\right)^{2}} \: , \quad j = 1, 2, 3 \: ,
\label{eq:dlambda}
\end{equation}
where 
$\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, $\tilde{r}_{3} = \tilde{z}$,
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$.
This equation can be determined directly from equation
\ref{eq:quadric-confocal-triaxial-ell}. 
The spatial derivatives of $\lambda$ in the case of
prolate or oblate ellipsoids can also be calculated by using
Equation \ref{eq:dlambda}, but with semi-axes $a > b = c$
or $b = c > a$, respectively.

>>>>

For triaxial ellipsoids (e.g., $a > b > c$), the demagnetization
factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] \: ,
\label{eq:n-tilde-dagger-11-triaxial}
\end{equation}
\begin{equation}
\tilde{n}^{\dagger}_{22} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( a^{2} - b^{2} \right)} 
\left[ F(\kappa, \phi) - E(\kappa, \phi) \right] + 
\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi)
- \frac{c^{2}}{b^{2} - c^{2}}
\label{eq:n-tilde-dagger-22-triaxial}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{33} = 
-\frac{abc}
{\left( a^{2} - c^{2} \right)^{\frac{1}{2}} 
\left( b^{2} - c^{2} \right)} E(\kappa, \phi) +
\frac{b^{2}}{b^{2} - c^{2}} \: ,
\label{eq:n-tilde-dagger-33-triaxial}
\end{equation}
where $\kappa = \left[ \left( a^{2} - b^{2} \right) / 
\left( a^{2} - c^{2} \right) \right]^{\frac{1}{2}}$,
$\cos \phi = c/a$,
\begin{equation}
F(\kappa, \phi) = 
\int^{\phi}_{0} 
\frac{1}{\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}}
d\psi \: ,
\label{eq:F-kappa-phi}
\end{equation}
and
\begin{equation}
E(\kappa, \phi) = 
\int^{\phi}_{0} 
\left( 1 - \kappa^{2} \sin^{2} \psi \right)^{\frac{1}{2}}
d\psi \: .
\label{eq:E-kappa-phi}
\end{equation}
The functions $F(\kappa, \phi)$ (Eq. \ref{eq:F-kappa-phi}) and 
$E(\kappa, \phi)$ (Eq. \ref{eq:E-kappa-phi}) are
called Legendre's normal elliptic integrals of the first and 
second kind, respectivelly. \citet{stoner1945} presented a 
detailed deduction of the demagnetization factors $\tilde{n}^{\dagger}_{11}$
(Eq. \ref{eq:n-tilde-dagger-11-triaxial}), $\tilde{n}^{\dagger}_{22}$
(Eq. \ref{eq:n-tilde-dagger-22-triaxial}) and $\tilde{n}^{\dagger}_{33}$
(Eq. \ref{eq:n-tilde-dagger-33-triaxial}). \citet{clark1986} presented similar
formulas, but without any proof.

@@

For prolate ellipsoids (e.g., $a > b = c$), the demagnetization
factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = \frac{1}{m^{2} - 1}
\left\lbrace \frac{m}{\left( m^{2} - 1 \right)^{\frac{1}{2}}}
\ln \left[ m + \left( m^{2} - 1 \right)^{\frac{1}{2}} \right]
- 1 \right\rbrace
\label{eq:n-tilde-dagger-11-prolate}
\end{equation}
and
\begin{equation}
\tilde{n}^{\dagger}_{22} = \frac{1}{2} \left(1 - \tilde{n}^{\dagger}_{11} \right) \: ,
\label{eq:n-tilde-dagger-22-prolate}
\end{equation}
where $\tilde{n}^{\dagger}_{33} = \tilde{n}^{\dagger}_{22}$, 
which uses the $\tilde{n}^{\dagger}_{11}$ defined in 
Equation \ref{eq:n-tilde-dagger-11-prolate}, and $m = a/b$.
The detailed deduction of the demagnetization factors 
$\tilde{n}^{\dagger}_{11}$ (Eq. \ref{eq:n-tilde-dagger-11-prolate}) 
and $\tilde{n}^{\dagger}_{22}$ (Eq. \ref{eq:n-tilde-dagger-22-prolate})
can be found, for example, in \citet{stoner1945}. 
These formulas were posteriorly 
presented by \citet{emerson1985}, but without any mathematical proof.

@@

For oblate ellipsoids (e.g., $a < b = c$), the demagnetization
factors obtained by solving Equation \ref{eq:n-tilde-dagger-ii} 
are given by:
\begin{equation}
\tilde{n}^{\dagger}_{11} = 
\frac{1}{1 - m^{2}} \left[
1 - \frac{m}{\left( 1 - m^{2} \right)^{\frac{1}{2}}} \cos^{-1}m
\right] \: ,
\label{eq:n-tilde-dagger-11-oblate}
\end{equation}
where $\tilde{n}^{\dagger}_{22}$ and $\tilde{n}^{\dagger}_{33}$ 
are calculated according to Equation
\ref{eq:n-tilde-dagger-22-prolate}, but with $\tilde{n}^{\dagger}_{11}$ 
defined in Equation \ref{eq:n-tilde-dagger-11-oblate}, 
and $m = a/b$.
The detailed deduction of these demagnetization factors 
can be found, for example, in \citet{stoner1945}. These formulas can also be found
in \citet{emerson1985}, but without any mathematical proof.
The only difference, however, is that \citet{emerson1985} replaced
the term $\cos^{-1}$ by a term $\tan^{-1}$, according to 
the trigonometric identity 
$\tan^{-1}x = \cos^{-1}(1/\sqrt{x^{2} + 1})$, $x > 0$.

@@

The elements $\tilde{n}^{\ddagger}_{ij}(\tilde{\mathbf{r}})$,
$i = 1, 2, 3$, $j = 1, 2, 3$, of the transformed depolarization tensor 
$\tilde{\mathbf{N}}^{\ddagger}(\tilde{\mathbf{r}})$ used to compute
the magnetic field $\Delta \tilde{\mathbf{H}}(\tilde{\mathbf{r}})$ 
(Eq. \ref{eq:delta-H-tilde}) and
the total-field anomaly $\Delta \tilde{T}(\tilde{\mathbf{r}})$
(Eqs. \ref{eq:delta-T-tilde} and \ref{eq:delta-T-tilde-approx}) 
are calculated according to Equation \ref{eq:nij-tilde}, with 
$\tilde{f}(\tilde{\mathbf{r}})$ given by $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
(Eq. \ref{eq:fe-tilde}).

@@

In the case of oblate ellipsoids, the procedure for determining
the parameter $\lambda$ is very similar to this one for prolate
ellipsoids.
The semi-axes $a$, $b$, $c$ of oblate 
ellipsoids are defined so that $b = c > a > 0$
and the condition that must be fulfilled by 
the variable $u$ is $u + a^{2} > 0$.
In this case, the two roots of the resulting quadratic equation 
lie in the intervals $[ -b^{2} \, , -a^{2} ]$ and $[ -a^{2} \, , \infty [$.
Consequently, we are still interested in the largest root of
the quadratic equation for the variable $u$, which is also 
calculated by using Equation \ref{eq:lambda-prolate-ell}.

@@

Let us first consider a triaxial ellipsoid. In this case,
the spatial derivatives of $\lambda$ are given by
\begin{equation}
\frac{\partial \lambda}{\partial \tilde{r}_{j}} =
\frac{\frac{2 \, \tilde{r}_{j}}{\left( e_{j}^{2} + \lambda \right)}}{
\left( \frac{\tilde{x}}{a^{2} + \lambda}\right)^{2} +
\left( \frac{\tilde{y}}{b^{2} + \lambda}\right)^{2} + 
\left( \frac{\tilde{z}}{c^{2} + \lambda}\right)^{2}} \: , \quad j = 1, 2, 3 \: ,
\label{eq:dlambda}
\end{equation}
where 
$\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, $\tilde{r}_{3} = \tilde{z}$,
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$.
This equation can be determined directly from equation
\ref{eq:quadric-confocal-triaxial-ell}. 
The spatial derivatives of $\lambda$ in the case of
prolate or oblate ellipsoids can also be calculated by using
Equation \ref{eq:dlambda} for the particular case in
with $b = c$.
